---
title: "Module Template"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

Welcome to our template module. Every module comprises a series of topical *tutorials*, such as the three linked below.

1. [First Topic](/tutorials/first_topic/index.qmd)
1. [Second Topic](/tutorials/next_topic/index.qmd)
1. [Third Topic](/tutorials/last_topic/index.qmd)

Each tutorial will comprise a series of interactive lessons with practice problems embedded throughout. Each tutorial
section should be wrapped up with a knowledge quiz.

## Learning Goals

After completing this module, you will be able to:

### Topic 1

1. A thing you should learn about Topic 1.
1. Another thing you should learn about Topic 1.
1. One more thing you should learn about Topic 1.

### Topic 2

1. A thing you should learn about Topic 2.
1. Another thing you should learn about Topic 2.

### Topic 3

1. A thing you should learn about Topic 3.
1. Another thing you should learn about Topic 3.
1. One more thing you should learn about Topic 3.
1. Yet more stuff you should learn about Topic 3.

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/first_topic/index.html")
```
